
\documentclass[11pt]{article}

% Set the margins to be something normal.
\usepackage[margin=1in]{geometry}

% Fun lists!
\usepackage{enumitem}
\usepackage{textcomp}
\setitemize{label=\textrightarrow, itemsep=0pt}

% Math symbols.
\usepackage{amsmath, amssymb, amsfonts}

% No indents.
\setlength\parindent{0pt}

% Nice fonts :)
\usepackage{tgschola}

\begin{document}

	\thispagestyle{empty}

	\Large{MATH:114, Recitations 309 and 310} \\
	\large{Lesson plan for August 24\textsuperscript{th}} \\
	
	\begin{description}[leftmargin=8em,style=nextline]
		\item[5-10 minutes] Go through the \textbf{intro slides}, introducing Anthony to the class, establishing class principles, answering initial questions.
		\item[15 minutes] Have groups of 3-4 work through the \textbf{Welcome worksheet}, based on Dana C. Ernst's ``setting the stage'' activity. This is a physical worksheet, and each group of students should sign it (for attendance). The primary goal is to get students to interact with each other, get a feel for the classroom atmosphere, and think about how they can adapt their learning styles to an inquiry-based classroom. A secondary goal is to get the energy level up (via collaboration, maybe some debate), especially considering recitations are (a) at night and (b) immediately after dinner.
		\item[Leftovers] Have groups of 3-4 go through the \textbf{Week 1 worksheet} problems at their whiteboards; each instructor should cover 4-5 groups and help them transition from the previous activity to the new one. These problems should follow from what happened in lecture the previous day. The goal is to get students re-familiarized with:
		
			\begin{itemize}
				\item what quadratic and linear functions look like, and drawing them
				\item finding the intersection point(s) of two or more curves
				\item finding limits of integration in the $x$ and $y$ directions
				\item integrating the right functions over the right limits of integration.
			\end{itemize}
			
			We'll assist with problems as needed.
			
		\item[Closing] Each group should turn in their Welcome worksheet. Encourage students to give feedback in the Week 1 Journal on Blackboard. Answering questions for $\sim$5 minutes after class ends is okay; after 309 we need to prep for the next group, for 310 we want to go home!

	\end{description}

	
	

\end{document}
