
\documentclass[12pt]{article}

% Set the margins to be something normal.
\usepackage[margin=1in]{geometry}

% Fun lists!
\usepackage[normalem]{ulem}
\usepackage{enumitem}
\usepackage{textcomp}
\setitemize{label=\textrightarrow, itemsep=0pt}

% Math symbols.
\usepackage{amsmath, amssymb, amsfonts}

% No indents.
\setlength\parindent{0pt}

% Nice fonts :)
\usepackage{tgschola}

\begin{document}
	\thispagestyle{empty}
	
	{\huge{Welcome to recitation for \textsc{MATH}:114!}} \\[1em]
	{\Large{Keep this sheet --- each group should turn in a copy at the end of class.}} \\[2em]
	
	Team members: \uline{\hfill} \\[1em]
	\phantom{}\uline{\hfill} \\[2em]
	
	\textbf{Individually}, take 1-2 minutes to think about these questions. After you've thought about answers, discuss them with your teammates.
	
	\begin{enumerate}
		\item What is something \textit{not math-related} that you're good at? How did you get good at it?
		\item How do \textit{you} learn something new?
		\item What's the value of making mistakes while learning?
		\item What makes you feel confident in a learning environment?
	\end{enumerate} \vspace{2em}
	
	\textbf{Individually}, take 1-2 minutes to answer these questions. Then, \textbf{as a team}, take five minutes to discuss them, possibly using answers to previous questions.
	
	\begin{enumerate}
		\item What is the best experience you've had working in a group? What's the worst one?
		\item What's one thing a teammate can do to help you succeed in this class?
		\item What's one thing \textit{you} can do to help others succeed in this class?
	\end{enumerate}
	
	\vspace{2em}
	
	After you've finished talking about these questions, \textbf{come up with three things a team can do to be successful} and write them on your whiteboard. We'll then talk about your ideas as a class!


\end{document}
